Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-04-20 VegOzone.tex
Add figure and finish other props

\subsubsection{Soil conditions}
\label{subsec:soil}

@@

The estimate of leaf boundary layer resistance is a function of wind speed which will be influenced by the tree height and leaf dimensions. A sample of downy birch leaves collected at Svanhovd had an average length of $(3.0\pm 0.5)\,\unit{cm}$ that is smaller than in the MM parameterization. \citet[][p.~52]{NINA2004} indicate an average tree height of $13.5\,\unit{m}$ in the area. One Scots pine forest at Svanhovd has been studied as a part of the ICP Forest mapping. Heights were measured in 2004 when the stand was 90 years old. Mean tree height was $10.1\,\unit{m}$ and maximum height was $16.2\,\unit{m}$ (V. Timmerman, personal communication, June 2020). We used $13.5\,\unit{m}$ height for both deciduous and coniferous trees.

>>>>

\subsubsection{Other properties}
\label{subsec:soil}

@@

The quasi-laminar boundary layer resistance $R_b$ is a function of wind speed $u$ which is influenced by the tree height and leaf dimensions. For comparison with MM dimensions, we collected a sample of birch leaves. The birch (B. pubescence) leaves were collected from the outer canopy (good light exposure) of tall trees at two sites in Finnmark. The leaves were collected late in July so they were fully expanded. They were collected by hand, so at about $2\,\mathrm{m}$ height. As the sun is at a low elevation angle for most of the time in the growing season in this area, light exposure at the top of the tree is not expected to be different from lower leaves as long as they grow in a part of the tree that is not shadowed by other trees. At the first site (Karasjok), three leaves were collected from each of five adult trees. At the second site (Svanvik), five leaves were collected from one tree. The leaves were pressed and dried before scanning for the area and shape determination through image analysis. ImageJ was used for thresholding the images to give silhouettes of the leaves. After scaling the images, the program was used for finding the minimum Feret diameter. This measure finds the largest width of a leaf at a $90^\circ$ angle to the length of the leaf (the Feret diameter). With this method we found that the 20 leaves had a mean width of $(3.0\pm 0.5)\,\unit{cm}$ that is smaller than in the MM parameterization.

A report by \citet[][p.~52]{NINA2004} indicate an average tree height of $13.5\,\unit{m}$ in the Svanhovd area. One Scots pine forest at Svanhovd has been studied as a part of the ICP Forest mapping. Heights were measured in 2004 when the stand was 90 years old. Mean tree height was $10.1\,\unit{m}$ and maximum height was $16.2\,\unit{m}$ (V. Timmerman, personal communication, June 2020). We used $13.5\,\unit{m}$ height for both deciduous and coniferous trees as this number better represents a larger region and diversity of species.
